{\LARGE {\color{red}PLACEHOLDER-TITLE:} Functional Linear Regression in a Scalar-on-Function Setting with Applications to SOMETHING}

### 2021-11-15 main.tex
Increment

	\section{Theory}

	To understand functional linear regression and the differences between the methods presented in this paper, it is necessary to introduce some concepts and extend known aspects of linear regression theory to include functional objects. One integral concept in inferential statistics are random variables. Paraphrasing a definition by \cite{bauer_wahrscheinlichkeitstheorie_2020}, a random variable $X:\Omega \rightarrow \Omega'$ is an $\mathcal{A} \text{-} \mathcal{A'} \text{-measurable}$ function, where $(\Omega, \mathcal{A}, P)$ is a probability space and $(\Omega', \mathcal{A'})$ is a measure space.\\
	A typical case known to every undergraduate student of economics in less formal detail is $(\Omega', \mathcal{A'}) = (\mathbb{R}, \mathcal{B})$, where $\mathcal{B}$ is the canonical $\sigma$-algebra on the real numbers. As a first intuition, it is possible to imagine a similar concept where a random variable does not realize as an element of the real numbers but as a function in a function space. A formalization of this idea makes some more theoretical considerations necessary. The following theoretical introduction closely follows chapters 2.3 and 2.4 from \cite{hsing_theoretical_2015}.

	\subsection{Inner Products and Hilbert Spaces}
	A function $\langle \cdot, \cdot \rangle$ on a vector space $\mathbb{V}$ is called an inner product, if $\forall v, v_1, v_2 \in \mathbb{V}$ and $a_1, a_2 \in \mathbb{R}$ the following properties hold.
	\begin{multicols}{2}
			\begin{enumerate}
			\item $\langle v, v \rangle \geq 0$
			\item $\langle v, v \rangle = 0$ if $v = 0$
			\item $\langle a_1 v_1 = a_2 v_2, v \rangle = a_1 \langle v_1, v \rangle + a_2 \langle v_2, v \rangle$
			\item $\langle v_1, v_2 \rangle = \langle v_2, v_1 \rangle$
		\end{enumerate}
	\end{multicols}
	A vector space with an associated inner product is called an inner product space. {\color{red}[verbatim quote!]}
	The inner product naturally defines a norm and an associated distance on the vector space as follows.

>>>>

	\section{Theory}
	In multivariate regression, data is often observed in the form of elements from Euclidean space, $\mathbb{R}^p$. However, the statistics derived from infinite-dimensional random functions cannot be defined on a finite dimensional space. To understand functional linear regression and the differences between the methods presented in this paper, it is therefore necessary to introduce some concepts and extend known aspects of linear regression theory to include functional objects. One integral concept in inferential statistics are random variables. Paraphrasing a definition by \cite{bauer_wahrscheinlichkeitstheorie_2020}, a random variable $X:\Omega \rightarrow \Omega'$ is an $\mathcal{A} \text{-} \mathcal{A'} \text{-measurable}$ function, where $(\Omega, \mathcal{A}, P)$ is a probability space and $(\Omega', \mathcal{A'})$ is a measure space.\\
	A typical case known to every undergraduate student of economics in less formal detail is $(\Omega', \mathcal{A'}) = (\mathbb{R}, \mathcal{B})$, where $\mathcal{B}$ is the canonical $\sigma$-algebra on the real numbers. As a first intuition, it is possible to imagine a similar concept where a random variable does not realize as an element of the real numbers but as a function in a function space. A formalization of this idea makes some more theoretical considerations necessary. The following theoretical introduction closely follows chapters 2.3 and 2.4 from \cite{hsing_theoretical_2015}.

	\subsection{Inner Products and Hilbert Spaces}
	Let $\mathbb{V}$ be a vector space over some field of scalars $\mathbb{F}$. A function $\langle \cdot, \cdot \rangle : \mathbb{V} \times  \mathbb{V} \rightarrow \mathbb{F}$ is called an inner product, if $\forall v, v_1, v_2 \in \mathbb{V}$ and $a_1, a_2 \in \mathbb{F}$ the following properties hold.
	\begin{multicols}{2}
			\begin{enumerate}
			\item $\langle v, v \rangle \geq 0$
			\item $\langle v, v \rangle = 0$ if $v = 0$
			\item $\langle a_1 v_1 = a_2 v_2, v \rangle = a_1 \langle v_1, v \rangle + a_2 \langle v_2, v \rangle$
			\item $\langle v_1, v_2 \rangle = \langle v_2, v_1 \rangle$
		\end{enumerate}
	\end{multicols}
	A vector space with an associated inner product is called an inner product space. {\color{red}[verbatim quote!]}
	The inner product naturally defines a norm and an associated distance on the vector space as follows. In the following we will restrict our analysis to the case of $\mathbb{F} = \mathbb{R}$.
